Actuator line modeling of vertical-axis turbines

### 2016-05-04 paper.tex
Make Bachant corresponding address
Add more BR CFD refs

\corraddr{M.~Wosnik, Chase Ocean Engineering Laboratory, University of New
Hampshire, 24 Colovos Rd., Durham, NH, 03824, USA. \\
E-mail: martin.wosnik@unh.edu}

@@

Reynolds-averaged Navier--Stokes (RANS) turbulence models computed on 3-D
body-fitted (blade-resolved) grids can do a good job predicting the mean
performance and near-wake structure of a VAT, though their effectiveness depends
on the turbulence model applied~\cite{Bachant2016-BR-CFD}. However, 3-D
blade-resolved RANS presents a huge computational expense---on the order of
1,000 CPU hours per simulated second with contemporary hardware---since it must
resolve fine details of the blade boundary layers, which will preclude its use
for array analysis until the availability of computing power increases
sufficiently. It is therefore necessary to explore simpler models that can
predict the turbine loading and flow field with acceptable fidelity, but that
are economical enough to not require high performance computing, at least for
individual devices.

>>>>

\corraddr{P.~Bachant, Chase Ocean Engineering Laboratory, University of New
Hampshire, 24 Colovos Rd., Durham, NH, 03824, USA. \\
E-mail: pxL3@unh.edu}

@@

Reynolds-averaged Navier--Stokes (RANS) turbulence models computed on 3-D
body-fitted (blade-resolved) grids can do a good job predicting the mean
performance and near-wake structure of a VAT, though their effectiveness depends
on the turbulence model
applied~\cite{Bachant2016-BR-CFD,Lam2016,Alaimo2015,Boudreau2015}. However, 3-D
blade-resolved RANS presents a huge computational expense---on the order of
1,000 CPU hours per simulated second with contemporary hardware---since it must
resolve fine details of the blade boundary layers, which will preclude its use
for array analysis until the availability of computing power increases
sufficiently. It is therefore necessary to explore simpler models that can
predict the turbine loading and flow field with acceptable fidelity, but that
are economical enough to not require high performance computing, at least for
individual devices.
